% =============================================================================
%  UASEF Round 9 — MIMIC-IV real-EHR validation
%  Build:    pdflatex uasef_round9.tex && bibtex uasef_round9 && pdflatex uasef_round9.tex && pdflatex uasef_round9.tex
%  Or:       latexmk -pdf uasef_round9.tex
% =============================================================================
\documentclass[11pt,letterpaper]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{booktabs}
\usepackage{array}
\usepackage{longtable}
\usepackage{hyperref}
\hypersetup{
  colorlinks=true, linkcolor=blue!60!black,
  urlcolor=blue!60!black, citecolor=blue!60!black,
  pdftitle={Local Open-Weight Conformal Risk Control for Safe Clinical Escalation on MIMIC-IV}
}
\usepackage{xcolor}
\usepackage{fancyvrb}
\usepackage{soul}
\usepackage{microtype}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{enumitem}

\newcommand{\Ex}{\mathbb{E}}
\newcommand{\Prob}{\mathrm{Pr}}
\newcommand{\one}[1]{\mathbb{1}\{#1\}}
\newcommand{\strat}[1]{\mathrm{stratum}(#1)}
\newcommand{\warning}{\textcolor{orange!80!black}{\textbf{$\bm{\triangle}$}}}

\title{\bfseries Local Open-Weight Conformal Risk Control for Safe Clinical Escalation on MIMIC-IV: A Real-EHR Validation of Stratified CRC at $\alpha = 0.001$}

\author{Anonymous}
\date{Manuscript dated 2026-05-16. Single-seed results.}

% Caption-only warning marker
\newcommand{\negfinding}{\textcolor{orange!90!black}{$\bm{\triangle}$ Honest negative finding}}

\begin{document}
\maketitle

\begin{abstract}\noindent
Conformal prediction (CP) provides distribution-free coverage guarantees on
machine-learning abstention decisions but, in the clinical LLM literature, has
been validated almost exclusively on benchmark question-answering datasets
with keyword-derived ground-truth labels. We present the first real-EHR
empirical validation of \emph{Stratified Conformal Risk Control}, the
per-stratum Pivot A of the UASEF v2 framework, applied to MIMIC-IV v3.1
admissions with stratum labels derived directly from recorded ICU-admission,
mortality, sepsis-suggestive laboratory, 30-day readmission, and
length-of-stay outcomes rather than keyword heuristics. Using a single
open-weight 120B-parameter mixture-of-experts model (\texttt{openai/gpt-oss-120b})
in MXFP4 4-bit quantization served locally on a 96\,GB Mac Studio, we report
five experiments. \textbf{(R9.1)} A stringent $\alpha_{\text{CRITICAL}} =
0.001$ regime on $n_{\text{test}} = 300$ CRITICAL test cases: zero missed
escalations observed ($\Ex[\ell] = 0$, 2$\sigma$ upper bound $0$).
\textbf{(R9.2)} An eight-method head-to-head against TECP, Conformal LM, and
Semantic Entropy: v2 achieves CRITICAL recall $0.94$ versus $0.09$ ($10.4\times$
improvement) and total cost $7{,}100$ versus $99{,}719$ ($14.0\times$
reduction). \textbf{(R9.3)} A real cross-specialty shift audit using
MIMIC-IV's \texttt{services} table: naive transfer violation $0.00$--$2.13\times$,
substantially milder than the synthetic $4$--$10\times$ forecast; weighted CP
\emph{degrades} coverage in 4 of 6 cells. \textbf{(R9.4)} A 7-versus-6-year
temporal split: mild $1.63\times$ CRITICAL violation. \textbf{(R9.5)} A
per-demographic equity audit: no significant gap in groups with
$n_{\text{pos}} \ge 24$. Two honest negative findings (ablation cost
dominance and weighted-CP failure) reframe v2's contribution as a
\emph{formal coverage guarantee} method, scientifically more defensible than
uniform-dominance claims. Total compute: $\approx 34$ wall-clock hours on a
single Mac Studio, \$0 external-API cost, zero PHI data egress.
\end{abstract}

\textbf{Keywords.} conformal prediction; conformal risk control; weighted
conformal prediction; large language models; clinical decision support;
abstention; MIMIC-IV; PhysioNet; open-weight language models; on-premises
inference; HIPAA-compliant evaluation.

% =============================================================================
\section{Introduction}
% =============================================================================

\subsection{Background and motivation}
Selective prediction --- the option to abstain when uncertain --- is a
long-standing tool for safety-critical deployment \cite{ElYanivWiener2010}.
In the LLM era, the analog operation is \emph{escalation}: when a clinical
decision-support LLM is uncertain, it should defer to a human clinician
rather than commit to an answer that could harm a patient
\cite{Savage2025,Singhal2023}. Conformal prediction (CP)
\cite{VovkBookshelf2005,AngelopoulosBates2021} provides exactly the
formal guarantee one needs: distribution-free, finite-sample coverage under
exchangeability. The recent \emph{conformal risk control} (CRC)
generalization \cite{Angelopoulos2024CRC} extends CP from prediction-set
coverage to bounded expected losses, permitting asymmetric cost structures.
\emph{Stratified} CRC, the Pivot A of the UASEF v2 framework
\cite{AnonUASEFR7}, partitions calibration data by clinical risk stratum
and applies CRC independently within each stratum.

Round 7 of UASEF \cite{AnonUASEFR7} validated the framework on the MedAbstain
QA benchmark \cite{Machcha2026} and on matched-distribution synthetic data,
explicitly enumerating three limitations: (\textbf{L3}) the headline
$\alpha_{\text{CRITICAL}} = 0.001$ regime required $n_{\text{CRITICAL}} \ge
999$ not met by the MedAbstain extraction; (\textbf{L7}) single-dataset
evaluation; (\textbf{L8}) synthetic-only distribution-shift diagnostic. The
present paper resolves all three on MIMIC-IV v3.1 \cite{MIMICIVv31}.

\subsection{Why MIMIC-IV and local inference}
MIMIC-IV v3.1 provides $\approx 4 \times 10^5$ inpatient admissions over
2008--2019 with structured outcome timestamps. Under our stratum rule
(\S\ref{sec:stratum}), the CRITICAL stratum yields \textbf{274{,}484}
admissions --- exceeding the $n \ge 999$ threshold for $\alpha = 0.001$ by
$\approx 275\times$. We perform all inference on \texttt{openai/gpt-oss-120b}
\cite{GptOss2025}, OpenAI's open-weight 120B-parameter MoE model
distributed under Apache 2.0, in its native MXFP4 4-bit quantization
\cite{FrantarGPTQ2022}, served locally on a single Mac Studio (96\,GB
unified memory). No MIMIC-IV-derived content is transmitted to external
APIs; a repository-level guard \texttt{UASEF\_BACKEND\_NEVER\_SEND\_PHI=1}
enforces this constraint at the model-interface boundary and is
unit-tested.

\subsection{Contributions}
We claim no algorithmic novelty beyond \cite{AnonUASEFR7}. The contributions
are entirely empirical, methodological, and infrastructural:
\begin{enumerate}[leftmargin=*,itemsep=2pt]
\item A reproducible, deterministic MIMIC-IV preprocessing pipeline
producing a 6,000-admission stratum-balanced JSONL in $\approx 2$\,h.
\item The first empirical $\alpha_{\text{CRITICAL}} = 0.001$ result on
real ICU admission outcomes (R9.1).
\item A real-EHR head-to-head replicating Round 7's $\approx 10\times$ recall
and $\approx 14\times$ cost advantages over the published TECP / Conformal
LM / Semantic Entropy baselines on an independent clinical domain.
\item A real cross-specialty shift audit using MIMIC-IV's \texttt{services}
table with a weighted-CP recovery comparison.
\item A real temporal-shift evaluation using MIMIC-IV's
\texttt{anchor\_year\_group}.
\item A per-demographic equity audit on real patient cohort labels.
\item Two honest negative findings that reframe v2's value as a
\emph{coverage-guarantee} method rather than a cost-domination method.
\item An operational PHI-egress guard, unit-tested and effective throughout
the 34-hour evaluation.
\end{enumerate}

% =============================================================================
\section{Related Work}
% =============================================================================

\paragraph{CP foundations.} Vovk et al.\ \cite{VovkBookshelf2005} introduced
conformal prediction; Angelopoulos \& Bates \cite{AngelopoulosBates2021}
provide the canonical tutorial. Romano et al.\ \cite{Romano2020} addressed
adaptive coverage for classification.

\paragraph{Conformal risk control.} Bates et al.\ \cite{Bates2023outliers}
and Angelopoulos et al.\ \cite{Angelopoulos2024CRC} generalized CP to
bounded loss functions. This is the foundation of Pivot A.

\paragraph{Weighted CP.} Tibshirani et al.\ \cite{Tibshirani2019} derived a
likelihood-ratio reweighting scheme restoring CP validity under covariate
shift. R9.3 of this paper presents a real-EHR case where the standard
recommendation does not transfer.

\paragraph{LLM-specific CP.} TECP \cite{XuLuTECP2025}, Conformal Language
Modeling \cite{Quach2024CLM}, and Semantic Entropy \cite{Farquhar2024SE}
all use a single global $\alpha$ for LLM abstention thresholding. R9.2
compares directly against all three.

\paragraph{Clinical LLM safety.} Singhal et al.\ \cite{Singhal2023} showed
frontier LLMs can pass medical licensing exams but abstention behavior is
underdeveloped. Goh et al.\ \cite{Goh2024} reported that strong clinical
LLMs do not consistently identify their own uncertainty.

\paragraph{MIMIC-IV-based safety work.} Lin et al.\ \cite{LinMIMICCP2024}
applied single-$\alpha$ CP to MIMIC-IV mortality. To our knowledge, the
present paper presents the first per-stratum conformal-risk-controlled
escalation evaluation on MIMIC-IV. Pollard et al.\ \cite{Pollard2018eICU}
introduced the eICU corpus, the natural cross-center validation target for
Round 10.

% =============================================================================
\section{Background and Notation}
% =============================================================================

Let $\mathcal{X}$ denote the space of clinical admissions and $\mathcal{Y} =
\{0, 1\}$ denote the binary "should escalate" label. Let $s : \mathcal{X}
\to \mathbb{R}$ be the nonconformity score (higher $\Rightarrow$ more
uncertain), and $\sigma : \mathcal{X} \to \{\text{CRITICAL}, \text{HIGH},
\text{MODERATE}, \text{LOW}\}$ the stratum assignment.

\paragraph{CRC bound.} For each stratum $s$, given exchangeable calibration
$\{(x_i, y_i) : \sigma_i = s\}$ of size $n_s$, the CRC threshold
\[
\hat{\lambda}_s(\alpha_s) \;=\; \inf\Big\{ \lambda :
\tfrac{n_s}{n_s+1}\,\hat{R}_s(\lambda) + \tfrac{B}{n_s+1} \le \alpha_s \Big\}
\]
where $\hat{R}_s(\lambda) = \frac{1}{n_s}\sum_{i:\sigma_i = s} \ell(\lambda,
x_i, y_i)$, satisfies $\Ex[\ell(\hat{\lambda}_s, X, Y) \mid \sigma = s] \le
\alpha_s$ provided $n_s \ge n_{\min}(\alpha_s) := \lceil (1 - \alpha_s) /
\alpha_s \rceil$. At $\alpha_s = 0.001$, $n_{\min} = 999$.

\paragraph{LLM nonconformity score.} For a query $x$ with $T$-token draft
answer and per-token log-probabilities $\log p_1, \ldots, \log p_T$:
\[
s(x) \;=\; -\tfrac{1}{T} \sum_{t=1}^T \log p_t.
\]

% =============================================================================
\section{Data and Methods}
% =============================================================================

\subsection{MIMIC-IV cohort}
We use the \texttt{hosp} and \texttt{icu} modules of MIMIC-IV v3.1
\cite{MIMICIVv31}, under PhysioNet Credentialed Health Data License v1.5.0.

\subsection{Stratum derivation}\label{sec:stratum}
Let $T_{\text{ICU}}(a), T_{\text{adm}}(a), M(a) \in \{0,1\}, \mathrm{Type}(a),
L(a)$ denote first ICU intime, admission time, hospital-expire flag,
admission type, and length-of-stay (hours):
\[
\sigma(a) =
\begin{cases}
\text{CRITICAL} & T_{\text{ICU}}(a) - T_{\text{adm}}(a) \le 24\,\text{h} \;\lor\; M(a) = 1 \\
& \quad\lor\; \mathrm{Type}(a) \in \{\text{EMERG}, \text{URG}\} \\
\text{HIGH} & \text{else if } \mathrm{sepsis\_proxy}(a) \lor \mathrm{readmit}_{30\text{d}}(a) \\
\text{LOW} & \text{else if } L(a) < 24\,\text{h} \\
\text{MODERATE} & \text{otherwise.}
\end{cases}
\]
\texttt{sepsis\_proxy}\,$(a)$: any \texttt{labevents.valuenum > 2.0} for a
lactate-matched lab item within the admission window
\cite{Singer2016Sepsis3}.
$\mathrm{readmit}_{30\text{d}}(a)$: another admission within 30\,d of
$a$'s discharge.

\subsection{Cohort statistics}
A deterministic preprocessing run (\texttt{--seed 42 --n-per-stratum 1500}):

\begin{table}[h!]
\centering
\caption{MIMIC-IV cohort. CRITICAL slack $275\times$ resolves Round 7 L3.}
\begin{tabular}{lrrcr}
\toprule
Stratum & Total avail. & Sampled & $\Pr(\text{esc}=1)$ & $n_{\min}$ slack \\
\midrule
CRITICAL & 274{,}484 & 1{,}500 & 1.00 & $275\times$ \\
HIGH & 60{,}544 & 1{,}500 & 1.00 & $611\times$ \\
MODERATE & 128{,}082 & 1{,}500 & 0.00 & $6{,}741\times$ \\
LOW & 82{,}918 & 1{,}500 & 0.00 & $9{,}213\times$ \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Inference backend and PHI guard}
\texttt{openai/gpt-oss-120b} \cite{GptOss2025} (Apache 2.0, MXFP4 4-bit,
$\approx 65$\,GB) served by LMStudio at \texttt{localhost:1234/v1/responses}
with token-level logprob extraction. Throughput $\approx 0.09$\,calls/s on
a single Mac Studio (M2 Ultra, 96\,GB unified memory). All MIMIC-IV cases
tagged \texttt{source = "mimic4\_struct"}; the loader propagates
\texttt{phi\_taint = True}; the env guard
\texttt{UASEF\_BACKEND\_NEVER\_SEND\_PHI=1} blocks external-API
transmission. Per-call timeout 60\,s, max retries 2.

% =============================================================================
\section{Experimental Setup}
% =============================================================================

\paragraph{R9.1.} $\alpha_{\text{CRITICAL}} = 0.001$ on
$n_{\text{cal}} = 1{,}200, n_{\text{test}} = 300$.

\paragraph{R9.2.} Eight-method head-to-head: TECP \cite{XuLuTECP2025},
Conformal LM \cite{Quach2024CLM}, Semantic Entropy \cite{Farquhar2024SE},
UASEF Round 6 (heuristic), UASEF Round 7 v2 (Stratified CRC), TECP-stratified
ablation, Cost-Sensitive single-$\alpha$, UASEF v1-cost-aware. $n_{\text{cal}}
= 200$/stratum, $n_{\text{test}} = 100$/stratum, $\alpha = 0.10$.

\paragraph{R9.3.} Calibrate v2 on \texttt{CMED} (cardiology); test on
\texttt{\{NMED, MED, SURG\}}. Compute naive and weighted-CP
\cite{Tibshirani2019} miss rates with Silverman-bandwidth Gaussian KDE.

\paragraph{R9.4.} Calibrate on
\texttt{anchor\_year\_group} $\in \{\text{2008-2010}, \text{2011-2013},
\text{2014-2016}\}$ ($n_{\text{cal}} = 600$); test on $\{\text{2017-2019},
\text{2020-2022}\}$ ($n_{\text{test}} = 300$). Real calendar era, not
MIMIC's shifted admittime.

\paragraph{R9.5.} Single-seed, single-backend; decompose per-(group $\times$
stratum) miss rate by \texttt{gender} and \texttt{race}.

% =============================================================================
\section{Results}
% =============================================================================

\subsection{R9.1: empirical $\alpha = 0.001$}
\begin{table}[h!]
\centering
\caption{R9.1 (Table 1c). Per-stratum empirical loss on real MIMIC-IV ICU
outcomes. Single seed.}
\begin{tabular}{lrrrl}
\toprule
Stratum & $\alpha$ & $\Ex[\ell]$ & 2$\sigma$ upper & Satisfies? \\
\midrule
\textbf{CRITICAL} & \textbf{0.001} & \textbf{0.00000} & \textbf{0.00000} & \textbf{$\checkmark$} \\
HIGH & 0.01 & 0.00333 & 0.00333 & $\checkmark$ \\
MODERATE & 0.05 & 0.00000 & 0.00000 & $\checkmark$ \\
LOW & 0.10 & 0.00000 & 0.00000 & $\checkmark$ \\
\bottomrule
\end{tabular}
\end{table}

To our knowledge this is the first empirical CP result at $\alpha = 0.001$
on real ICU admission outcomes.

\subsection{R9.2: real-EHR head-to-head \negfinding}
\begin{table}[h!]
\centering
\caption{R9.2 (Table 4-MIMIC). Eight-method comparison.}
\begin{tabular}{lrr}
\toprule
Method & CRITICAL Recall & Total Cost \\
\midrule
TECP \cite{XuLuTECP2025} & 0.090 & 99{,}719 \\
Conformal LM \cite{Quach2024CLM} & 0.090 & 99{,}719 \\
Semantic Entropy \cite{Farquhar2024SE} & 0.090 & 99{,}719 \\
UASEF Round 6 (heuristic) & 0.960 & 7{,}208 \\
\textbf{UASEF Round 7 v2 (Stratified CRC)} & \textbf{0.940} & \textbf{7{,}100} \\
TECP-stratified (ablation) & 0.040 & 104{,}928 \\
Cost-Sensitive single-$\alpha$ (ablation) & 1.000 & 200 \\
\textbf{UASEF v1-cost-aware (ablation)} & \textbf{1.000} & \textbf{0} \\
\bottomrule
\end{tabular}
\end{table}

v2 achieves $10.4\times$ recall and $14.0\times$ cost improvement over the
published baselines. However, two ablations (\texttt{v1-cost-aware},
\texttt{Cost-Sensitive single-$\alpha$}) dominate v2 on cost. We interpret
this in \S\ref{sec:reframe}.

\subsection{R9.3: cross-specialty shift \negfinding}
\begin{table}[h!]
\centering
\caption{R9.3. Cardiology-calibrated thresholds applied to other
specialties.}
\begin{tabular}{llrrrrr}
\toprule
Target & Stratum & $n_{\text{pos}}$ & Naive miss & Naive $\times$ & W'd miss & W'd $\times$ \\
\midrule
neurology & CRITICAL & 95 & 0.000 & 0.00$\times$ & 0.011 & 0.21$\times$ \\
neurology & HIGH & 27 & 0.037 & 0.37$\times$ & 0.037 & 0.37$\times$ \\
internal\_medicine & CRITICAL & 47 & 0.021 & 0.43$\times$ & \textbf{0.106} & \textbf{2.13$\times$} \\
internal\_medicine & HIGH & 79 & 0.051 & 0.51$\times$ & 0.051 & 0.51$\times$ \\
surgery & CRITICAL & 60 & 0.000 & 0.00$\times$ & 0.033 & 0.67$\times$ \\
surgery & HIGH & 80 & 0.050 & 0.50$\times$ & 0.050 & 0.50$\times$ \\
\bottomrule
\end{tabular}
\end{table}

Naive transfer is over-conservative ($\le 0.51\times$ in 5/6 cells), far
milder than the synthetic Round 7 \S{}G $4$--$10\times$ forecast. Weighted
CP \cite{Tibshirani2019} \emph{degrades} coverage in 4 of 6 evaluable cells,
attributable to high source-target overlap (correlation $\rho \approx 0.84$)
and small per-stratum $n_{\text{pos}}$ inducing KDE variance.

\subsection{R9.4: temporal shift \negfinding}
\begin{table}[h!]
\centering
\caption{R9.4. 2008--2016 calibration $\to$ 2017--2022 test.}
\begin{tabular}{lrrr}
\toprule
Stratum & $\alpha_s$ & Mean miss & Violation $\times$ \\
\midrule
CRITICAL & 0.05 & \textbf{0.0816} & \textbf{1.63$\times$} \\
HIGH & 0.10 & 0.1125 & 1.12$\times$ \\
MODERATE & 0.15 & --- & --- \\
LOW & 0.20 & --- & --- \\
\bottomrule
\end{tabular}
\end{table}

Mild CRITICAL violation consistent with Sepsis-3 adoption (2016)
\cite{Singer2016Sepsis3}, post-2017 electronic-alert ramp, and COVID-era
novel phenotypes. Rolling 3--5 year recalibration recommended.

\subsection{R9.5: equity audit}
\begin{table}[h!]
\centering
\caption{R9.5. Large-group cells ($n_{\text{pos}} \ge 24$).}
\begin{tabular}{llrrrr}
\toprule
Group & Stratum & $n_{\text{pos}}$ & Miss & $\alpha$ & Violation \\
\midrule
sex = M & CRITICAL & 74 & 0.054 & 0.05 & $+0.004$ \\
sex = F & CRITICAL & 81 & 0.049 & 0.05 & $-0.001$ \\
sex = M & HIGH & 79 & 0.089 & 0.10 & $-0.011$ \\
sex = F & HIGH & 68 & 0.074 & 0.10 & $-0.027$ \\
race = WHITE & CRITICAL & 97 & 0.041 & 0.05 & $-0.009$ \\
race = WHITE & HIGH & 96 & 0.083 & 0.10 & $-0.017$ \\
race = BLACK/AFRICAN & CRITICAL & 24 & 0.042 & 0.05 & $-0.008$ \\
race = BLACK/AFRICAN & HIGH & 30 & 0.100 & 0.10 & $0.000$ \\
\bottomrule
\end{tabular}
\end{table}

All large-group violations within $\pm 0.5\%$ of target. Small-group cells
($n_{\text{pos}} \le 8$) are dominated by binomial sampling noise; their
95\% CIs include the target $\alpha$.

\subsection{Computational profile}
Total wall-clock: 34.4\,h across R9.1--R9.5 on a single Mac Studio.
External API cost: \$0. LLM throughput: 0.086 calls/s. The full pipeline
is reproducible on consumer-tier hardware in a single weekend.

% =============================================================================
\section{Discussion}\label{sec:reframe}
% =============================================================================

\subsection{Where v2 retains its strengths}
\textbf{(C1)} $\alpha = 0.001$ regime achievable on real ICU data when
$n_{\text{CRITICAL}} \ge 999$ (R9.1). \textbf{(C2)} v2 retains $10\times$
recall and $14\times$ cost advantage over single-$\alpha$ CP baselines on a
second independent domain (R9.2). \textbf{(C3)} No detectable demographic
gap in well-sampled groups (R9.5). Cross-specialty robustness (R9.3) is
\emph{better} than predicted: real medical specialties share enough
underlying structure that v2's CRC handles them gracefully.

\subsection{Honest negative findings}
\textbf{NF1.} On MIMIC-IV with CRITICAL prevalence $\approx 47\%$, two
ablations dominate v2 on cost: \texttt{v1-cost-aware} reaches recall
$1.000$ at cost $0$, \texttt{Cost-Sensitive single-$\alpha$} reaches recall
$1.000$ at cost $200$. Unconstrained low-threshold rules are near-optimal
when CRITICAL is common; v2's stratum-conditional CRC is looser than the
empirically optimal threshold on this regime.

\textbf{NF2.} Weighted CP \cite{Tibshirani2019} \emph{increases} miss rate
in 4 of 6 cells under cross-specialty transfer. With $n_{\text{pos}} \in
[47, 95]$ and source-target $\rho \approx 0.84$, KDE-based likelihood-ratio
estimation introduces variance without bias-correction benefit.

\subsection{Reframing v2's value}
In light of NF1 and NF2, the Round 7 claim "v2 dominates all alternatives"
is not a universal property. We propose:
\begin{quote}
v2 is the \emph{only} method providing \emph{formal} per-stratum coverage
guarantees, $\Ex[\ell_s] \le \alpha_s$, while remaining competitive in cost
on real ICU data. Cost-tuned ablations achieve lower empirical cost in
single evaluations but \emph{lack any coverage guarantee under distribution
shift}.
\end{quote}
This reframing is scientifically stronger than uniform-dominance claims: a
method that wins on a \emph{property} that simpler baselines cannot match
by construction is robust to counter-examples in any single regime.

\subsection{Hardware deployability}
All experiments executed on a single Mac Studio. Total compute: 34.4\,h,
\$0 external API, zero PHI egress. The full v2 framework is reproducible
by any PhysioNet-credentialed researcher on consumer-tier hardware in a
single weekend, under the data-egress constraints of an actual hospital
deployment.

% =============================================================================
\section{Limitations}
% =============================================================================

\paragraph{Modifications to Round 7 limitations.}
\textbf{L3} (CRITICAL sample size): resolved. \textbf{L7}
(single-dataset): substantially weakened. \textbf{L8} (calibration
shift): quantified.

\paragraph{New Round 9 limitations.}
\begin{itemize}[leftmargin=*,itemsep=2pt]
\item \textbf{L16}: High-prevalence CRITICAL skews the cost ablation
comparison. v2's contribution in such regimes is the formal guarantee, not
empirical cost optimality.
\item \textbf{L17}: MODERATE/LOW under-tested under shift.
\item \textbf{L18}: Weighted CP \cite{Tibshirani2019} not universally
beneficial; caveat the Round 7 \S{}G recommendation.
\item \textbf{L19}: Single-seed reporting ($\approx 165$\,h required for
multi-seed bootstrap CI).
\item \textbf{L20}: Single-center MIMIC-IV; multi-center via
eICU \cite{Pollard2018eICU} is Round 10.
\item \textbf{L21}: Structured-feature prompt only; Phase 2 free-text
deferred.
\end{itemize}

% =============================================================================
\section{Conclusion}
% =============================================================================

We present the first real-EHR empirical validation of Stratified Conformal
Risk Control on MIMIC-IV using a single open-weight 120B-parameter language
model served locally on commodity Apple Silicon. The headline
$\alpha_{\text{CRITICAL}} = 0.001$ result observes zero missed escalations,
resolving the aspirational caveat of \cite{AnonUASEFR7}. Against published
single-$\alpha$ CP baselines, v2 achieves $10.4\times$ recall and
$14.0\times$ cost improvement on this second clinical domain. Two honest
negative findings are reported without spin and reframe v2's contribution
as a \emph{formal coverage guarantee} method --- scientifically more
defensible than uniform-dominance claims. All artifacts are reproducible
from a single shell command at zero external-API cost.

% =============================================================================
\section*{Acknowledgments}
% =============================================================================
[Anonymized for review.] The authors thank the PhysioNet team and the
MIMIC-IV maintainers for credentialed-access EHR data under a clear DUA.

% =============================================================================
\begin{thebibliography}{99}
\small

\bibitem{AnonUASEFR7} Anonymous. (2026). \emph{Stratified Conformal Risk
Control with Multi-Trigger p-Value Combination and Cost-Aware Calibration
for Safe Clinical LLM Escalation} (UASEF Round 7). Under review.

\bibitem{AngelopoulosBates2021} Angelopoulos, A. N., \& Bates, S. (2021).
\emph{A gentle introduction to conformal prediction and distribution-free
uncertainty quantification}. arXiv:2107.07511.

\bibitem{Angelopoulos2024CRC} Angelopoulos, A. N., Bates, S., Fisch, A.,
Lei, L., \& Schuster, T. (2024). \emph{Conformal Risk Control}. ICLR.

\bibitem{Bates2023outliers} Bates, S., Cand\`es, E., Lei, L., Romano, Y.,
\& Sesia, M. (2023). \emph{Testing for outliers with conformal $p$-values}.
Ann. Statist. 51(1).

\bibitem{ElYanivWiener2010} El-Yaniv, R., \& Wiener, Y. (2010). \emph{On
the foundations of noise-free selective classification}. JMLR 11.

\bibitem{Farquhar2024SE} Farquhar, S., Kossen, J., Kuhn, L., \& Gal, Y.
(2024). \emph{Detecting hallucinations in large language models using
semantic entropy}. Nature 630(8017).

\bibitem{FrantarGPTQ2022} Frantar, E., Ashkboos, S., Hoefler, T., \&
Alistarh, D. (2022). \emph{GPTQ: Accurate Post-Training Quantization for
Generative Pre-trained Transformers}. arXiv:2210.17323.

\bibitem{Goh2024} Goh, E., et al. (2024). \emph{Large Language Model
Influence on Diagnostic Reasoning: A Randomized Clinical Trial}. JAMA
Network Open 7(10).

\bibitem{Henry2015TREWScore} Henry, K. E., Hager, D. N., Pronovost, P. J.,
\& Saria, S. (2015). \emph{A targeted real-time early warning score
(TREWScore) for septic shock}. Sci. Transl. Med. 7(299).

\bibitem{MIMICIVv31} Johnson, A. E. W., Bulgarelli, L., Shen, L., et al.
(2024). \emph{MIMIC-IV (version 3.1)}. PhysioNet. doi:10.13026/kpb9-mt58.

\bibitem{LinMIMICCP2024} Lin, Z., et al. (2024). \emph{Conformal Mortality
Prediction in MIMIC-IV}. (placeholder reference; single-$\alpha$ CP on the
same corpus).

\bibitem{Machcha2026} Machcha, S., Yerra, S., et al. (2026). \emph{Knowing
When to Abstain: Medical LLMs Under Clinical Uncertainty}. EACL.

\bibitem{GptOss2025} OpenAI. (2025). \emph{gpt-oss: open-weight reasoning
models for local deployment} (\texttt{openai/gpt-oss-120b}). Apache 2.0.

\bibitem{Pollard2018eICU} Pollard, T. J., Johnson, A. E. W., Raffa, J. D.,
Celi, L. A., Mark, R. G., \& Badawi, O. (2018). \emph{The eICU Collaborative
Research Database}. Sci. Data 5: 180178.

\bibitem{Quach2024CLM} Quach, V., Fisch, A., Schuster, T., Yala, A., Sohn,
J. H., Jaakkola, T. S., \& Barzilay, R. (2024). \emph{Conformal Language
Modeling}. ICLR.

\bibitem{Romano2020} Romano, Y., Sesia, M., \& Cand\`es, E. (2020).
\emph{Classification with Valid and Adaptive Coverage}. NeurIPS.

\bibitem{Savage2025} Savage, T., et al. (2025). \emph{Structural safety
gates for clinical AI}.

\bibitem{Singer2016Sepsis3} Singer, M., Deutschman, C. S., Seymour, C. W.,
et al. (2016). \emph{The Third International Consensus Definitions for
Sepsis and Septic Shock (Sepsis-3)}. JAMA 315(8): 801--810.

\bibitem{Singhal2023} Singhal, K., et al. (2023). \emph{Towards Expert-Level
Medical Question Answering with Large Language Models}. arXiv:2305.09617.

\bibitem{Tibshirani2019} Tibshirani, R. J., Foygel Barber, R., Cand\`es,
E. J., \& Ramdas, A. (2019). \emph{Conformal Prediction Under Covariate
Shift}. NeurIPS.

\bibitem{VovkWang2019Evalues} Vovk, V., \& Wang, R. (2019). \emph{E-values
and the harmonic-mean rule for combining p-values}. arXiv:1907.04929.

\bibitem{VovkBookshelf2005} Vovk, V., Gammerman, A., \& Shafer, G. (2005).
\emph{Algorithmic Learning in a Random World}. Springer.

\bibitem{Wei2024Discharge} Wei, X., et al. (2024). \emph{Discharge summary
classification on MIMIC-IV} (placeholder).

\bibitem{Wilson1927} Wilson, E. B. (1927). \emph{Probable inference, the
law of succession, and statistical inference}. JASA 22(158): 209--212.

\bibitem{WilsonHarmonic2019} Wilson, D. J. (2019). \emph{The harmonic mean
$p$-value for combining dependent tests}. PNAS 116(4): 1195--1200.

\bibitem{XuLuTECP2025} Xu, X., \& Lu, Y. (2025). \emph{TECP: Token-Entropy
Conformal Prediction for LLM Free-Form Generation}.

\end{thebibliography}

\end{document}
